Results

### 2023-04-16 writeups/results.qmd
put code at bottom
added summary
updated config options

```{r}
#| echo: false
############################ Parameters to set ############################
model_name <- "sv_user_guide_reparameterised_ksc_priors_ksc_phi_0.97779_sig_0.1585_beta_0.64733_"
pp_flag <- "posterior" # prior = no likelihood estimation, posterior = likelihood estimation

# Data location
data_loc <- "simulated"
data_type <- "ksc"
file_name <- "phi_0.97779_sig_0.1585_beta_0.64733"
############################ Parameters to set ############################
```

@@

path <- here::here("output", model_name)
rds_path <- list.files(path = here::here("output", model_name), full.names = TRUE, pattern = "*.RDS")
csv_path <- list.files(path = here::here("output", model_name), full.names = TRUE, pattern = "*.csv")

@@

# Load training data
data <- read.csv(here::here("data", data_loc, data_type, paste(file_name, ".csv", sep = "")))
dependent_variable <- "yobs" # log squared returns
returns <- data[complete.cases(data[dependent_variable]), dependent_variable]

@@

@@

## Model code

@@

>>>>

```{r}
#| echo: false
source(here::here("config.r"))

############################ Parameters to set ############################
if (!(config)) {
output_name <- "sv_user_guide_reparameterised_ksc_priors_ksc_phi_0.97779_sig_0.1585_beta_0.64733_"
pp_flag <- "posterior" # prior = no likelihood estimation, posterior = likelihood estimation

# Data location
data_loc <- "simulated"
data_type <- "ksc"
data_file_name <- "phi_0.97779_sig_0.1585_beta_0.64733"
}
############################ Parameters to set ############################
```

@@

path <- here::here("output", output_name)
rds_path <- list.files(path = here::here("output", output_name), full.names = TRUE, pattern = "*.RDS")
csv_path <- list.files(path = here::here("output", output_name), full.names = TRUE, pattern = "*.csv")

@@

# Load training data
data <- read.csv(here::here("data", data_loc, data_type, paste(data_file_name, ".csv", sep = "")))
dependent_variable <- "yobs" # log squared returns
returns <- data[complete.cases(data[dependent_variable]), dependent_variable]

@@

<!-- ```{r}
model_fit$summary()
``` -->

@@

```{r}
#| echo: false
#| output: 'asis'
paste(pp_flag, output_name, sep = " ")
```

@@

# Model code

# Model sampling time

```{r}
# Time to sample
model_fit$time()
```

# Model console messages

```{r}
# Console messages
model_fit$output()
```
